Meta-Analysis of the `Ironic' Effects of Intergroup Contact

### 2021-06-18 manuscript/manuscript.Rmd
submit

---
title: "Meta-Analysis of the 'Ironic' Effects of Intergroup Contact"
header: "'IRONIC' EFFECTS META-ANALYSIS"
keywords: intergroup contact, meta-analysis, perceived discrimination, collective action, policy support
bibliography: references.bib
csl: apa.csl
nocite: | 
  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005
abstract: 
  Growing evidence suggests that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, has the ‘ironic’ effect of reducing support for social change in disadvantaged groups. We conducted a preregistered meta-analytic test of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members. As predicted, intergroup contact was, on average, associated with less perceived injustice (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "pi"]), digits = 2), "$"))`), collective action (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ca"]), digits = 2), "$"))`), and support for reparative policies (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ps"]), digits = 2), "$"))`). However, these associations were small, variable, and consistent with alternative explanations. Across outcomes, `r with(readRDS("../results/results_for_abstract.rds"), paste0(round(min(p_pred)*100), "--", round(max(p_pred)*100), "\\%"))` of studies found *positive* associations with intergroup contact. Moderator analyses explained about a third of the between-sample variance, showing that, on average, associations were negative only in studies of adults that measured intergroup contact directly and were strongest in studies that examined short-term migration or (post-)colonial intergroup relations. We also found evidence for an alternative explanation for the apparent ‘ironic’ effects of intergroup contact as, after controlling for the positive association of negative contact with support for social change, positive contact was no longer associated with any of the outcomes. We close by discussing strengths and limitations of the available evidence and by highlighting open questions about the relationship between intergroup contact and support for social change in disadvantaged groups.
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: yes
    template: apa-template.tex
  word_document:
    reference_docx: word-template.docx
---

@@

Researchers have, however, argued that intergroup contact might *not* reduce support for social change and, in some circumstances, might even *increase* support for social change in disadvantaged groups.

@@

Other researchers have put forward alternative explanations for the apparent 'ironic' effects of intergroup contact. Whereas previous studies had focused on positive contact experiences, recent studies considered both positive and negative contact experiences as predictors of support for social change. Researchers [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions, suggesting that negative contact experiences motivate disadvantaged-group members to support social change. @956 further found that, first, disadvantaged-group members who have more positive contact also tend to have less negative contact and, second, positive contact is not associated with perceived discrimination or collective action after controlling for negative contact. Based on these findings, @956 argued that the mobilizing effect of negative contact could be an alternative explanation for the negative relationship between positive contact and support for social change observed in prior studies.

Another alternative explanation for the apparent 'ironic' effects of intergroup contact centers on intragroup contact. Whereas most studies focused on contact with the advantaged outgroup, some studies examined contact with the disadvantaged ingroup as a predictor of support for social change. @sengupta_ingroup_2015 found ingroup contact to be associated with decreased endorsement of system-justifying beliefs and increased support for reparative policies benefiting the disadvantaged ingroup, suggesting that contact with other ingroup members can motivate disadvantaged-group members to support social change [see also @1695]. As outgroup contact places limits on how much ingroup contact a person can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact. Based on these observations, one might argue that the mobilizing effect of ingroup contact could be an alternative explanation for the negative association between outgroup contact and support for social change observed in prior studies.

@@

We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcomes, using effect sizes from all studies that measured both predictors (Figure 8b). Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` studies, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "pi"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "pi"]`) with perceived injustice. Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` studies, we found stronger evidence for a positive association between ingroup contact and collective action (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "ca"]`) than for a negative association between outgroup contact and collective action (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "ca"]`). Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` study, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "ps"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "ps"]`) with policy support. Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "og"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "og"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "og"]` studies, we found a positive association between ingroup and outgroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "og"]`).

@@

To conclude, our preregistered meta-analysis found some evidence that intergroup contact reduces perceived injustice, discourages collective action, and diminishes support for reparative policies in disadvantaged groups—but also showed that the estimated effect sizes were small, variable, and consistent with alternative explanations. Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues to explain variance in these associations; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include measures that allow testing alternative explanations for the  apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis. We hope that our meta-analysis helps researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.

@@

\noindent References marked with an asterisk are studies included in the meta-analysis.

>>>>

---
title: "Meta-Analysis of the 'Ironic' Effects of Intergroup Contact"
header: "'IRONIC' EFFECTS META-ANALYSIS"
keywords: intergroup contact, meta-analysis, perceived discrimination, collective action, policy support
bibliography: references.bib
csl: apa.csl
nocite: | 
  @19, @45, @46, @91, @93, @244, @284, @286, @303, @322, @324, @325, @336, @401, @414, @423, @480, @609, @703, @733, @783, @789, @803, @813, @823, @829, @830, @856, @893, @894, @933, @956, @1020, @1042, @1045, @1114, @1163, @1221, @1248, @1376, @1386, @1395, @1407, @1411, @1412, @1494, @1525, @1549, @1576, @1614, @1658, @1695, @1743, @1762, @1807, @1850, @1891, @1914, @1949, @1966, @1993, @2001, @2023, @2033, @2075, @2257, @2309, @2333, @2341, @2375, @2380, @2381, @2382, @2383, @2385, @2391, @2392, @2394, @2395, @2396, @2397, @2398, @2399, @3000, @3005, @3051, @3054, @3060, @3134, @3196, @3201, @3205, @4000, @4001, @4002, @4003, @4004, @4005
abstract: 
  Growing evidence suggests that intergroup contact, psychology’s most-researched paradigm for reducing prejudice, has the ‘ironic’ effect of reducing support for social change in disadvantaged groups. We conducted a preregistered meta-analytic test of this effect across `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(dplyr::n_distinct(id)))` studies with `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(length(sample)))` samples of `r with(dplyr::distinct(readRDS("../data/dl.rds"), sample, id, n), numform::f_comma(sum(n)))` disadvantaged-group members. As predicted, intergroup contact was, on average, associated with less perceived injustice (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "pi"]), digits = 2), "$"))`), collective action (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ca"]), digits = 2), "$"))`), and support for reparative policies (`r with(readRDS("../results/results_preregistered_analyses.rds"), paste0("$r = ", numform::f_num(median(r_mean[x_var == "ic" & y_var == "ps"]), digits = 2), "$"))`). However, these associations were small, variable, and consistent with alternative explanations. Across outcomes, `r with(readRDS("../results/results_for_abstract.rds"), paste0(round(min(p_pred)*100), "--", round(max(p_pred)*100), "\\%"))` of studies found *positive* associations with intergroup contact. Moderator analyses explained about a third of the between-sample variance, showing that, on average, associations were negative only in studies of adults that measured intergroup contact directly and were strongest in studies that examined short-term migration or (post-)colonial intergroup relations. We also found evidence for an alternative explanation for the apparent ‘ironic’ effects of intergroup contact as, after controlling for the positive association of negative contact with support for social change, positive contact was no longer associated with any of the outcomes. We close by discussing strengths and limitations of the available evidence and by highlighting open questions about the relationship between intergroup contact and support for social change in disadvantaged groups.
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: yes
    template: apa-template.tex
---

@@

Others have, however, argued that intergroup contact might *not* reduce support for social change and, in some circumstances, might even *increase* support for social change in disadvantaged groups.

@@

Other researchers have put forward alternative explanations for the apparent 'ironic' effects of intergroup contact. Whereas previous studies had focused on positive contact experiences, recent studies considered both positive and negative contact experiences as predictors of support for social change. These studies [@2309; @956] found negative contact with advantaged-group members to be associated with greater perceived discrimination and stronger collective action intentions. This research suggests that negative contact can motivate disadvantaged-group members to support social change. @956 further found that, first, disadvantaged-group members who have more positive contact also tend to have less negative contact and, second, positive contact is not associated with perceived discrimination or collective action after controlling for negative contact. Based on these findings, @956 argued that the mobilizing effect of negative contact could be an alternative explanation for the negative relationship between positive contact and support for social change observed in prior studies.

Another alternative explanation for the apparent 'ironic' effects of intergroup contact centers on intragroup contact. Whereas most studies focused on contact with the advantaged outgroup, some studies examined contact with the disadvantaged ingroup as a predictor of support for social change. @levin_ethnic_2006 found that, among minority-group college students, ingroup friendship predicted perceived discrimination 1–2 years later. @sengupta_ingroup_2015 found ingroup contact to be associated with decreased endorsement of system-justifying beliefs and increased support for reparative policies benefiting the disadvantaged ingroup [see also @1695]. These studies suggest that contact with other ingroup members can motivate disadvantaged-group members to support social change. As outgroup contact places limits on how much ingroup contact a person can have [@pfister_contact_2020], disadvantaged-group members who have more outgroup contact can be expected to have less ingroup contact. Based on these observations, one might argue that the mobilizing effect of ingroup contact could be an alternative explanation for the negative association between outgroup contact and support for social change observed in prior studies.

@@

We ran three random-effects meta-analysis models that estimated the partial correlations of ingroup and outgroup contact with each outcome, using effect sizes from all studies that measured both predictors (Figure 8b). Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "pi"]` studies, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "pi"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "pi"]`) with perceived injustice. Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "ca"]` studies, we found stronger evidence for a positive association between ingroup contact and collective action (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "ca"]`) than for a negative association between outgroup contact and collective action (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "ca"]`). Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "ps"]` study, we found insufficient evidence for associations of ingroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "ps"]`) and outgroup contact (`r alt_results$text[alt_results$x_var == "og" & alt_results$y_var == "ps"]`) with policy support. Across `r alt_results$N[alt_results$x_var == "ig" & alt_results$y_var == "og"]` participants from `r alt_results$I[alt_results$x_var == "ig" & alt_results$y_var == "og"]` samples in `r alt_results$J[alt_results$x_var == "ig" & alt_results$y_var == "og"]` studies, we found a positive association between ingroup and outgroup contact (`r alt_results$text[alt_results$x_var == "ig" & alt_results$y_var == "og"]`).

@@

To conclude, our preregistered meta-analysis found some evidence that intergroup contact reduces perceived injustice, discourages collective action, and diminishes support for reparative policies in disadvantaged groups—but also showed that the estimated effect sizes were small, variable, and consistent with alternative explanations. Future research should (1) compare the direction and magnitude of the associations between intergroup contact and support for social change across cultures, groups, and issues; (2) use longitudinal designs and field experiments to establish the direction of these relationships and to rule out spurious associations; (3) include measures that allow testing alternative explanations for the apparent 'ironic' effects of intergroup contact; and (4) incorporate practices to prevent undisclosed flexibility in data collection and analysis. We hope that our meta-analysis helps researchers to address the open questions about how intergroup contact relates to support for social change in disadvantaged groups.

@@

References marked with an asterisk are studies included in the meta-analysis.

### 2021-06-18 manuscript/manuscript.tex
submit

% \maketitle
% 
% \newpage

@@

Researchers have, however, argued that intergroup contact might
\emph{not} reduce support for social change and, in some circumstances,
might even \emph{increase} support for social change in disadvantaged
groups.

@@

Other researchers have put forward alternative explanations for the
apparent `ironic' effects of intergroup contact. Whereas previous
studies had focused on positive contact experiences, recent studies
considered both positive and negative contact experiences as predictors
of support for social change. Researchers (Hayward et al., 2018; Reimer
et al., 2017) found negative contact with advantaged-group members to be
associated with greater perceived discrimination and stronger collective
action intentions, suggesting that negative contact experiences motivate
disadvantaged-group members to support social change. Reimer et al.
(2017) further found that, first, disadvantaged-group members who have
more positive contact also tend to have less negative contact and,
second, positive contact is not associated with perceived discrimination
or collective action after controlling for negative contact. Based on
these findings, Reimer et al. (2017) argued that the mobilizing effect
of negative contact could be an alternative explanation for the negative
relationship between positive contact and support for social change
observed in prior studies.

Another alternative explanation for the apparent `ironic' effects of
intergroup contact centers on intragroup contact. Whereas most studies
focused on contact with the advantaged outgroup, some studies examined
contact with the disadvantaged ingroup as a predictor of support for
social change. Sengupta et al. (2015) found ingroup contact to be
associated with decreased endorsement of system-justifying beliefs and
increased support for reparative policies benefiting the disadvantaged
ingroup, suggesting that contact with other ingroup members can motivate
disadvantaged-group members to support social change (see also Sengupta
\& Sibley, 2013). As outgroup contact places limits on how much ingroup
contact a person can have (Pfister et al., 2020), disadvantaged-group
members who have more outgroup contact can be expected to have less
ingroup contact. Based on these observations, one might argue that the
mobilizing effect of ingroup contact could be an alternative explanation
for the negative association between outgroup contact and support for
social change observed in prior studies.

@@

We ran three random-effects meta-analysis models that estimated the
partial correlations of ingroup and outgroup contact with each outcomes,
using effect sizes from all studies that measured both predictors
(Figure 8b). Across 6,888 participants from 15 samples in 8 studies, we
found insufficient evidence for associations of ingroup contact
(\(r = .03, [-.10, .15]\); \(\Pr (r > 0) = 69.0\%\)) and outgroup
contact (\(r = -.10, [-.26, .07]\); \(\Pr (r < 0) = 89.2\%\)) with
perceived injustice. Across 3,938 participants from 4 samples in 2
studies, we found stronger evidence for a positive association between
ingroup contact and collective action (\(r = .12, [.03, .20]\);
\(\Pr (r > 0) = 99.1\%\)) than for a negative association between
outgroup contact and collective action (\(r = -.08, [-.25, .10]\);
\(\Pr (r < 0) = 85.5\%\)). Across 3,187 participants from 3 samples in 1
study, we found insufficient evidence for associations of ingroup
contact (\(r = .09, [-.13, .27]\); \(\Pr (r > 0) = 86.2\%\)) and
outgroup contact (\(r = -.03, [-.12, .08]\); \(\Pr (r < 0) = 78.5\%\))
with policy support. Across 6,888 participants from 15 samples in 8
studies, we found a positive association between ingroup and outgroup
contact (\(r = .25, [.10, .34]\); \(\Pr (r > 0) = 99.7\%\)).

@@

To conclude, our preregistered meta-analysis found some evidence that
intergroup contact reduces perceived injustice, discourages collective
action, and diminishes support for reparative policies in disadvantaged
groups---but also showed that the estimated effect sizes were small,
variable, and consistent with alternative explanations. Future research
should (1) compare the direction and magnitude of the associations
between intergroup contact and support for social change across
cultures, groups, and issues to explain variance in these associations;
(2) use longitudinal designs and field experiments to establish the
direction of these relationships and to rule out spurious associations;
(3) include measures that allow testing alternative explanations for the
apparent `ironic' effects of intergroup contact; and (4) incorporate
practices to prevent undisclosed flexibility in data collection and
analysis. We hope that our meta-analysis helps researchers to address
the open questions about how intergroup contact relates to support for
social change in disadvantaged groups.

@@

>>>>

@@

Others have, however, argued that intergroup contact might \emph{not}
reduce support for social change and, in some circumstances, might even
\emph{increase} support for social change in disadvantaged groups.

@@

Other researchers have put forward alternative explanations for the
apparent `ironic' effects of intergroup contact. Whereas previous
studies had focused on positive contact experiences, recent studies
considered both positive and negative contact experiences as predictors
of support for social change. These studies (Hayward et al., 2018;
Reimer et al., 2017) found negative contact with advantaged-group
members to be associated with greater perceived discrimination and
stronger collective action intentions. This research suggests that
negative contact can motivate disadvantaged-group members to support
social change. Reimer et al. (2017) further found that, first,
disadvantaged-group members who have more positive contact also tend to
have less negative contact and, second, positive contact is not
associated with perceived discrimination or collective action after
controlling for negative contact. Based on these findings, Reimer et al.
(2017) argued that the mobilizing effect of negative contact could be an
alternative explanation for the negative relationship between positive
contact and support for social change observed in prior studies.

Another alternative explanation for the apparent `ironic' effects of
intergroup contact centers on intragroup contact. Whereas most studies
focused on contact with the advantaged outgroup, some studies examined
contact with the disadvantaged ingroup as a predictor of support for
social change. Levin et al. (2006) found that, among minority-group
college students, ingroup friendship predicted perceived discrimination
1--2 years later. Sengupta et al. (2015) found ingroup contact to be
associated with decreased endorsement of system-justifying beliefs and
increased support for reparative policies benefiting the disadvantaged
ingroup (see also Sengupta \& Sibley, 2013). These studies suggest that
contact with other ingroup members can motivate disadvantaged-group
members to support social change. As outgroup contact places limits on
how much ingroup contact a person can have (Pfister et al., 2020),
disadvantaged-group members who have more outgroup contact can be
expected to have less ingroup contact. Based on these observations, one
might argue that the mobilizing effect of ingroup contact could be an
alternative explanation for the negative association between outgroup
contact and support for social change observed in prior studies.

@@

We ran three random-effects meta-analysis models that estimated the
partial correlations of ingroup and outgroup contact with each outcome,
using effect sizes from all studies that measured both predictors
(Figure 8b). Across 6,888 participants from 15 samples in 8 studies, we
found insufficient evidence for associations of ingroup contact
(\(r = .03, [-.10, .15]\); \(\Pr (r > 0) = 69.0\%\)) and outgroup
contact (\(r = -.10, [-.26, .07]\); \(\Pr (r < 0) = 89.2\%\)) with
perceived injustice. Across 3,938 participants from 4 samples in 2
studies, we found stronger evidence for a positive association between
ingroup contact and collective action (\(r = .12, [.03, .20]\);
\(\Pr (r > 0) = 99.1\%\)) than for a negative association between
outgroup contact and collective action (\(r = -.08, [-.25, .10]\);
\(\Pr (r < 0) = 85.5\%\)). Across 3,187 participants from 3 samples in 1
study, we found insufficient evidence for associations of ingroup
contact (\(r = .09, [-.13, .27]\); \(\Pr (r > 0) = 86.2\%\)) and
outgroup contact (\(r = -.03, [-.12, .08]\); \(\Pr (r < 0) = 78.5\%\))
with policy support. Across 6,888 participants from 15 samples in 8
studies, we found a positive association between ingroup and outgroup
contact (\(r = .25, [.10, .34]\); \(\Pr (r > 0) = 99.7\%\)).

@@

To conclude, our preregistered meta-analysis found some evidence that
intergroup contact reduces perceived injustice, discourages collective
action, and diminishes support for reparative policies in disadvantaged
groups---but also showed that the estimated effect sizes were small,
variable, and consistent with alternative explanations. Future research
should (1) compare the direction and magnitude of the associations
between intergroup contact and support for social change across
cultures, groups, and issues; (2) use longitudinal designs and field
experiments to establish the direction of these relationships and to
rule out spurious associations; (3) include measures that allow testing
alternative explanations for the apparent `ironic' effects of intergroup
contact; and (4) incorporate practices to prevent undisclosed
flexibility in data collection and analysis. We hope that our
meta-analysis helps researchers to address the open questions about how
intergroup contact relates to support for social change in disadvantaged
groups.

@@

\leavevmode\hypertarget{ref-levin_ethnic_2006}{}%
Levin, S., Van Laar, C., \& Foote, W. (2006). Ethnic segregation and
perceived discrimination in college: Mutual influences and effects on
social and academic life. \emph{Journal of Applied Social Psychology},
\emph{36}(6), 1471--1501.
\url{https://doi.org/10.1111/j.0021-9029.2006.00068.x}
